---
title: "100-CA-loci"
output: html_document
date: "2023-08-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

Need to get list of loci and prepare fasta with [Major/Minor] identified and 250 bp flanking data.     

Looks like this:

```{r}
loci<-read_csv("meta/LCT_fixedSNPs_AF_perBasin_July12.csv")
loci
```

We want a tab-delimited input (sites.txt)      
Chrom  Site    Major   Minor MAF     
Frequency_LCT istead of MAF
```{r}
sites<- loci %>% select(Chromosome, Position, Major, Minor, Frequency_LCT)
sites
write_tsv(sites, col_names = FALSE, file="meta/LCT_fixedSNPs_AF_perBasin_July12.tsv")
```


Executing like so:    

`./100.1-extract-flanking.pl meta/LCT_fixedSNPs_AF_perBasin_July12.tsv > outputs/100/LCT_fixedSNPs_AF_perBasin_July12.fasta`     
 
 
 Making a .tsv version like so:
 
 `cat outputs/100/LCT_fixedSNPs_AF_perBasin_July12.fasta  | perl -pe 's/(\d)\n/$1\t/g' | perl -pe 's/>//g' > outputs/100/LCT_fixedSNPs_AF_perBasin_July12.tsv `
 
 